Age-related changes in plant growth and traits

### 2017-06-28 scripts/Accessory_figs_20160905.Rmd
Start revising Accessory costs MS

par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05)) 
plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=2)
segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="count, scaled to plant size",side=2,line=1.1,outer=FALSE,cex=0.8)
mtext(text="costs (mg/seed)",side=1,line=1.0,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("seed count by reproductive costs","initiated ovules count by pollen-attraction costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
extra.top.left("b",2,1)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="choosiness (ovule:seed)",side=2,line=1.3,outer=FALSE,cex=0.8)
mtext(text="pollen attraction costs,",side=1,line=1.1,outer=FALSE,cex=0.8)
mtext(text="scaled to plant size",side=1,line=1.9,outer=FALSE,cex=0.8)
extra.top.left("c",2,1)
dev.off()

@@

par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05))
plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=2)
axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
mtext(text="proportion all pollen-attraction investment",side=2,line=1.8,outer=FALSE,cex=0.8)
mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("become seeds","are aborted before provisioning"),title="into ovules that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
extra.top.left("d",2,1)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=2)
segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=1)
axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
mtext(text="proportion all provisioning investment",side=2,line=1.8,outer=FALSE,cex=0.8)
mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("become seeds","are aborted"),title="into zygotes that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
extra.top.left("e",2,1)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
segments(x0=.15,x1=.9,y0=.15,y1=.9,lty=2)
axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
mtext(text="proportion total success costs",side=2,line=1.8,outer=FALSE,cex=0.8)
mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("pollen-attraction costs","provisioning costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
extra.top.left("f",2,1)

@@

line_function_log_xy(SummarySpp[["mean"]]$repro_costs,mod_seed,1,col=venetian_red)
line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod_ovule,1,col=cerulean)
legend("bottomleft",legend=c("seed count by reproductive costs","mature ovules count by","pollen-attraction costs"),col=c(venetian_red,cerulean,"white"),pch=c(16,16,16),bty="n",cex=0.7)
extra.top.left.logxy("a",2,1)

#panel b
#plot(choosiness~prop_pollen_attract_vs_all_repro_all_repro,SummarySpp[["mean"]],log="xy",col=cerulean,pch=16,xlim=c(0.002,.5),ylim=c(3,800),xaxt="n",yaxt="n",cex=1,ylab="",xlab="")
plot(choosiness2~scaled_pollen_attract_costs,SummarySpp[["mean"]],log="xy",col=cerulean,pch=16,xlim=c(.002,.3),ylim=c(3,800),yaxt="n",cex=1,ylab="",xlab="",xaxt="n")
axis(2, at=c(10,100,1000), labels=c(10,100,1000),cex.axis=0.8,las=2)
axis(1, at=c(0.01,0.1), labels=c(0.01,0.1),cex.axis=0.8)
mtext("pollen-attractions costs, scaled to leaf area",1,line=1.7,cex=0.7)
mtext("choosiness (ovules:seed)",2,line=2.3,cex=0.7)
mod_choosy <- sma(choosiness2~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]]),log="xy",slope=-1,method="SMA")
mod_choosy2 <- sma(choosiness2~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",slope=-1,method="SMA")
line_function_log_xy(SummarySpp[["mean"]]$scaled_pollen_attract_costs,mod_choosy2,1,col=cerulean)
extra.top.left.logxy("b",2,1)

#panel c - success proportions
plot(prop_prepollen_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,ylim=c(-.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
points(prop_prepollen_discarded~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
#arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_success-SummarySpp[["se"]]$prop_prepollen_success,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_success+SummarySpp[["se"]]$prop_prepollen_success,code=3,angle=90, length=0.1,col=cerulean)
#arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_discarded-SummarySpp[["se"]]$prop_prepollen_discarded,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_discarded+SummarySpp[["se"]]$prop_prepollen_discarded,code=3,angle=90, length=0.1,col=venetian_red)
extra.top.left.logx("c",2,1)
axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
mtext("seed size (mg)",1,line=1.8,cex=0.7)
mtext("prop. total pollen-attraction investment",2,line=2.3,cex=0.7)
legend("bottomleft",legend=c("successful ovules","discarded ovules"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)

@@

#panel d - pollen-attraction proportions
plot(prop_postpollen_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
points(prop_postpollen_discarded~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
extra.top.left.logx("d",2,1)
axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
mtext("seed size (mg)",1,line=1.8,cex=0.7)
mtext("prop. total provisioning investment",2,line=2.3,cex=0.7)
legend("bottomleft",legend=c("successful zygotes","aborted zygotes"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)

@@

#panel e - provisioning proportions
plot(prop_pollen_attract_vs_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,
     ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
points(prop_provisioning_vs_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
#arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_pollen_attract_vs_success-SummarySpp[["se"]]$prop_pollen_attract_vs_success,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_pollen_attract_vs_success+SummarySpp[["se"]]$prop_pollen_attract_vs_success,code=3,angle=90, length=0.1,col=cerulean)
extra.top.left.logx("e",2,1)
axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
mtext("seed size (mg)",1,line=1.8,cex=0.7)
mtext("prop. successful investment",2,line=2.3,cex=0.7)
legend("bottomleft",legend=c("pollen attraction costs","provisioning costs"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)

@@

#panel f - change in slope of "success costs"
plot(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="xy",col=cerulean,xlim=c(.01,100),ylim=c(.01,20000),xlab="",ylab="",xaxt="n",yaxt="n")
points(provisioning_costs~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
extra.top.left.logxy("f",2,1)
axis(2, at=c(0.01,1,100,10000), labels=c(0.01,1,100,10000),cex.axis=0.8,las=2)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
mtext("seed size (mg)",1,line=1.8,cex=0.7)
mtext("success cost (mg/seed)",2,line=2.3,cex=0.7)
legend("bottomright",legend=c("pollen attraction","provisioning"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)

>>>>

par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05)) 
plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=2)
segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="count, scaled to plant size",side=2,line=1.1,outer=FALSE,cex=0.8)
mtext(text="costs (mg/seed)",side=1,line=1.0,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("seed count by reproductive costs","initiated ovules count by pollen-attraction costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
extra.top.left("b")

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="choosiness (ovule:seed)",side=2,line=1.3,outer=FALSE,cex=0.8)
mtext(text="pollen attraction costs,",side=1,line=1.1,outer=FALSE,cex=0.8)
mtext(text="scaled to plant size",side=1,line=1.9,outer=FALSE,cex=0.8)
extra.top.left("c")
dev.off()

@@

par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05))
plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=2)
axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
mtext(text="proportion all pollen-attraction investment",side=2,line=1.8,outer=FALSE,cex=0.8)
mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("become seeds","are aborted before provisioning"),title="into ovules that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
extra.top.left("d")

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=2)
segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=1)
axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
mtext(text="proportion all provisioning investment",side=2,line=1.8,outer=FALSE,cex=0.8)
mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("become seeds","are aborted"),title="into zygotes that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
extra.top.left("e")

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
segments(x0=.15,x1=.9,y0=.15,y1=.9,lty=2)
axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
mtext(text="proportion total success costs",side=2,line=1.8,outer=FALSE,cex=0.8)
mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("pollen-attraction costs","provisioning costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
extra.top.left("f")

@@

line_function_log_xy(SummarySpp[["mean"]]$repro_costs,mod_seed,1,col=venetian_red)
line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod_ovule,1,col=cerulean)
legend("bottomleft",legend=c("seed count by reproductive costs","mature ovules count by","pollen-attraction costs"),col=c(venetian_red,cerulean,"white"),pch=c(16,16,16),bty="n",cex=0.7)
extra.top.left.logxy("a")

#panel b
#plot(choosiness~prop_pollen_attract_vs_all_repro_all_repro,SummarySpp[["mean"]],log="xy",col=cerulean,pch=16,xlim=c(0.002,.5),ylim=c(3,800),xaxt="n",yaxt="n",cex=1,ylab="",xlab="")
plot(choosiness2~scaled_pollen_attract_costs,SummarySpp[["mean"]],log="xy",col=cerulean,pch=16,xlim=c(.002,.3),ylim=c(3,800),yaxt="n",cex=1,ylab="",xlab="",xaxt="n")
axis(2, at=c(10,100,1000), labels=c(10,100,1000),cex.axis=0.8,las=2)
axis(1, at=c(0.01,0.1), labels=c(0.01,0.1),cex.axis=0.8)
mtext("pollen-attractions costs, scaled to leaf area",1,line=1.7,cex=0.7)
mtext("choosiness (ovules:seed)",2,line=2.3,cex=0.7)
mod_choosy <- sma(choosiness2~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]]),log="xy",slope=-1,method="SMA")
mod_choosy2 <- sma(choosiness2~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",slope=-1,method="SMA")
line_function_log_xy(SummarySpp[["mean"]]$scaled_pollen_attract_costs,mod_choosy2,1,col=cerulean)
extra.top.left.logxy("b")

#panel c - success proportions
plot(prop_prepollen_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,ylim=c(-.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
points(prop_prepollen_discarded~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
#arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_success-SummarySpp[["se"]]$prop_prepollen_success,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_success+SummarySpp[["se"]]$prop_prepollen_success,code=3,angle=90, length=0.1,col=cerulean)
#arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_discarded-SummarySpp[["se"]]$prop_prepollen_discarded,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_discarded+SummarySpp[["se"]]$prop_prepollen_discarded,code=3,angle=90, length=0.1,col=venetian_red)
extra.top.left.logx("c")
axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
mtext("seed size (mg)",1,line=1.8,cex=0.7)
mtext("prop. total pollen-attraction investment",2,line=2.3,cex=0.7)
legend("bottomleft",legend=c("successful ovules","discarded ovules"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)

@@

#panel d - pollen-attraction proportions
plot(prop_postpollen_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
points(prop_postpollen_discarded~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
extra.top.left.logx("d")
axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
mtext("seed size (mg)",1,line=1.8,cex=0.7)
mtext("prop. total provisioning investment",2,line=2.3,cex=0.7)
legend("bottomleft",legend=c("successful zygotes","aborted zygotes"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)

@@

#panel e - provisioning proportions
plot(prop_pollen_attract_vs_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,
     ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
points(prop_provisioning_vs_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
#arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_pollen_attract_vs_success-SummarySpp[["se"]]$prop_pollen_attract_vs_success,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_pollen_attract_vs_success+SummarySpp[["se"]]$prop_pollen_attract_vs_success,code=3,angle=90, length=0.1,col=cerulean)
extra.top.left.logx("e")
axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
mtext("seed size (mg)",1,line=1.8,cex=0.7)
mtext("prop. successful investment",2,line=2.3,cex=0.7)
legend("bottomleft",legend=c("pollen attraction costs","provisioning costs"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)

@@

#panel f - change in slope of "success costs"
plot(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="xy",col=cerulean,xlim=c(.01,100),ylim=c(.01,20000),xlab="",ylab="",xaxt="n",yaxt="n")
points(provisioning_costs~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
extra.top.left.logxy("f")
axis(2, at=c(0.01,1,100,10000), labels=c(0.01,1,100,10000),cex.axis=0.8,las=2)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
mtext("seed size (mg)",1,line=1.8,cex=0.7)
mtext("success cost (mg/seed)",2,line=2.3,cex=0.7)
legend("bottomright",legend=c("pollen attraction","provisioning"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)
